%-------------------------
% Resume in Latex
% Author : Timothy O'Connor
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{multicol}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
        \textbf{\Huge \scshape Timothy O'Connor} \\ \vspace{1pt}
        \small 201-815-3901 $|$ \href{mailto:x@x.com}{\underline{tjo45@miami.edu}} $|$ 
        \href{https://www.linkedin.com/in/timothy-o-connor-a17223198/...}{\underline{https://www.linkedin.com/in}} $|$
        \href{https://github.com/timoconnnor...}{\underline{https://github.com}} $|$
        \href{https://tim-oconnor.com/}{\underline{https://tim-oconnor.com/}}
    \end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Miami}{Coral Gables, FL}
      {Bachelors in Quantitative Economics, Minors in Computer Science and Finance}{Aug. 2019 -- December 2023} 

    \vspace{10pt} % Adjust the value to control the amount of space

    \textbf{Relevant Coursework:}
      \begin{multicols}{2}
        \begin{itemize}
          \item Android Programming
          \item Data Structures and Algorithms
          \item Intro to Programming
          \item Mathematical Applications in Economics
          \item Advanced Macroeconomics
          \item Advanced Econometrics
        \end{itemize}
      \end{multicols}
  \resumeSubHeadingListEnd




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development and Finance Intern}{June 2021 -- August 2021}
      {Effectual Inc.}{Jersey City, NJ}
      \resumeItemListStart
        \resumeItem{Developed a REST API using FastAPI and PostgreSQL to store data from learning management systems}
        \resumeItem{Developed a full-stack web application using Flask, React, PostgreSQL and Docker to analyze GitHub data}
        \resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting}
      \resumeItemListEnd

      \resumeSubheading
      {Google Student Developer Club Member}{August 2019 -- Present}
      {University of Miami}{Coral Gables}
      \resumeItemListStart
        \resumeItem{Participated in various coding and development activities organized by the club}
        \resumeItem{Collaborated with fellow students on projects and coding challenges}
        \resumeItem{Attended workshops and events to enhance coding skills and knowledge}
      \resumeItemListEnd
      

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Simple Search Engine} $|$ \emph{Java}}{May 2023}
        \resumeItemListStart
          \resumeItem{Developed a search engine using all the structures and algorithms learned in class.}
          \resumeItem{Implemented efficient data structures for indexing and retrieval.}
          \resumeItem{Optimized search algorithms for faster query processing.}
          \resumeItem{Collaborated with team members to ensure smooth integration of features.}
\resumeItemListEnd

      \resumeProjectHeading
          {\textbf{NFL Machine Learning Sports Prediction} $|$ \emph{Python}}{August 2023 -- Present}
\resumeItemListStart
  \resumeItem{Designed and implemented a machine learning-based sports prediction system for NFL games.}
  \resumeItem{Objective: To outperform traditional predictions using algorithms and data analysis.}
  \resumeItem{Step-By-Step Breakdown:}
  \resumeItemListStart
    \resumeItem{Data Collection: Gathered historical NFL game data, including detailed statistics, team information, and game results. Utilized a web scraper for data extraction from pro football reference.}
    \resumeItem{Data Analysis: Employed machine learning algorithms to analyze the collected data and identify patterns.}
    \resumeItem{Model Training: Developed and trained predictive models using the processed data.}
    \resumeItem{Evaluation: Assessed the performance of the models through testing and validation processes.}
    \resumeItem{Iterative Improvement: Continuously refined the models based on feedback and updated data.}
  \resumeItemListEnd
\resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Hackathon Project - Water Consumption Tracker} $|$ \emph{Python}}{April 2023}
        \resumeItemListStart
          \resumeItem{Developed an innovative application during a hackathon to track water consumption based on the food consumed}
          \resumeItem{Utilized OpenAI's API to analyze food data and determine the corresponding water usage}
          \resumeItem{Designed and implemented a user-friendly website for deploying the application}
          \resumeItem{Collaborated with a team to integrate backend functionality and ensure seamless user experience}
          \resumeItem{Presented the project to judges and received positive feedback on its creativity and environmental impact}
        \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, Python, R, CSS, HTML} \\
     \textbf{Frameworks}{: React, Git, Linux} \\
     \textbf{Developer Tools}{: Git, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib} \\
     \textbf{Document Preparation:} LaTeX
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
